Univariate Analysis

### 2017-08-21 model fitting/cross_validation.Rmd
fitted splines and square root transformations of quantitative variables

```{r, echo = FALSE}
train1 <- x[splitPlan[[1]]$train, ]

@@

# backward/forward step-wise selection with stepAIC function from MASS package
model2 <- MASS::stepAIC(first, direction = "both", k = 2)
# results
results2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
AIC(results2, k = 2) # 65277.47
```

@@

```{r, echo = FALSE}
# adding title_questionmark*title_beginwh
model2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
AIC(model2, k = 2) # 65274.49
compare_nested(model2, results2)

@@

# adding new_user*ampm 
model2_2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*ampm, data = train1)
AIC(model2_2, k = 2) # 65271.84
compare_nested(model2_2, results2)

@@

model_new <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
AIC(model_new, k = 2) #64999.87

@@

#=============================================
#deviance residuals 
train1$deviance <- residuals(model_full, type = "deviance")
ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
  geom_point() + 
  scale_x_continuous("Question index") + 
  scale_y_continuous(breaks = seq(-4, 4, by = 0.5))
# quite a few questions have a deviance residual of larger than 2.5

@@

#=============================================
# formal test of PH assumption
ph_test <- data.frame(predictors = rownames(cox.zph(model_full)$table), cox.zph(model_full)$table) 
rownames(ph_test) = NULL
ph_test <- ph_test %>%
  arrange(p)

@@

@@

#==================================================================================================
# function to take in a data set, fit the model, output performance metrics, and allow you to specify times to predict survival probabilities

>>>>

```{r, echo = FALSE}
# write a function to set up variables for this training data

train1 <- x[splitPlan[[1]]$train, ]

@@

# backward/forward step-wise selection with stepAIC function from MASS package
model2 <- MASS::stepAIC(first, direction = "both", k = 2)
# results
results2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
AIC(results2, k = 2) # 65277.47
summary(results2)
```

@@

```{r, echo = FALSE}
# adding title_questionmark*title_beginwh
model2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
AIC(model2, k = 2) # 65274.49
oshitar::compare_nested(model2, results2)

@@

# adding new_user*ampm 
model2_2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*ampm, data = train1)
AIC(model2_2, k = 2) # 65271.84
oshitar::compare_nested(model2_2, results2)

@@

model_new <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
AIC(model_new, k = 2) #64999.87
summary(model_new)

@@

#=============================================
#deviance residuals 
train1$deviance <- residuals(model_full, type = "deviance")
ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
  geom_point() + 
  scale_x_continuous("Question index") + 
  scale_y_continuous(breaks = seq(-4, 4, by = 0.5)) + 
  ggtitle("Deviance Residuals")
# quite a few questions have a deviance residual of larger than 2.5

@@

#=============================================
# working with rms::which.influence to id influential points
c <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, x = TRUE, y = TRUE, data = train1)
influence <- rms::which.influence(c)
rms::show.influence(influence, train1)

#=============================================
# formal test of PH assumption
options(scipen=999)
ph_test <- data.frame(predictors = rownames(cox.zph(model_full)$table), cox.zph(model_full)$table) 
rownames(ph_test) = NULL
ph_test <- ph_test %>%
  arrange(p)

@@

### Checking multicolliniearity

```{r, echo = FALSE}
rms::vif()
```

@@

#==================================================================================
# function to take in a data set, fit the model, output performance metrics, and allow you to specify times to predict survival probabilities

### 2017-08-21 model fitting/univariate_analysis.Rmd
fitted splines and square root transformations of quantitative variables

#===================================================================
# n_tags
pvalues <- get_pvalue("n_tags")

@@

@@

#===================================================================
# newline ratio to length of text
train1$newline_ratio <- str_count(train1$text, pattern = "\n")/str_length(train1$text)
pvalues <- get_pvalue("newline_ratio")
```

@@

>>>>

#===================================================================
# n_tags
pvalues <- get_pvalue("n_tags", factor = TRUE)

@@

# splines
fit <- coxph(Surv(time_until_answer, answered) ~ pspline(title_length, df = 0, method = "AIC"), data = train1)
summary(fit) # p=0.2322

@@

#===================================================================
# newline ratio to length of text
train1$newline_ratio <- str_count(train1$text, pattern = "\n")/str_length(train1$text)
pvalues <- get_pvalue("newline_ratio")

ggplot2::ggplot(train1, aes(x = time_until_answer, y = newline_ratio)) + 
  geom_point()
```

@@

### researching splines

* spline: piecewise m - 1 degree polynomial that is continuous up to its first m - 2 derivatives
* obtain more flexible curves: increase the degree of spline/add more knots
* tradeoff: 
    + few knots/low degree: class of functions may be too restrictive (bias)
    + many knots/high degree: risk overfitting 
* spline has m + K degrees of freedom 
* types of splines
    + cubic splines (most common)
* truncated power basis - flawed
* B-spline basis: much more stable, typically used 
* Natural cubic splines
    + polynomial fits tend to be erratic at boundaries of data (even worse for cubic splines)
    + natural cubic splines fix this by adding 4 constraints that the function is linear beyond the boundaries of the data 
    + because basis functions are fixed, model fitting and inference are straightforward exentsions to how the model would normally be without splines

```{r, echo = FALSE}
# fit splines + sqrt/log transformations on title_length, text_length, device_length, avg_tag_length, newline_ratio

# title_length
fit <- coxph(Surv(time_until_answer, answered) ~ pspline(title_length, df = 0, method = "AIC"), data = train1)
summary(fit) # p=0.2322

fit1 <- coxph(Surv(time_until_answer, answered) ~ sqrt(title_length), data = train1)
summary(fit1) # p=0.4874

# text_length
fit2 <- coxph(Surv(time_until_answer, answered) ~ pspline(text_length, df = 0, method = "AIC"), data = train1)
summary(fit1) # p=0
fit3 <- coxph(Surv(time_until_answer, answered) ~ sqrt(text_length), data = train1)
summary(fit2) # p=0.000000000000000111
AIC(fit2, k = 2) # 65867.02
fit4 <- coxph(Surv(time_until_answer, answered) ~ log10(text_length), data = train1)
summary(fit3) # p=0.000000000000000111
AIC(fit3, k = 2) # 65862.83

# device_length
fit5 <- coxph(Surv(time_until_answer, answered) ~ pspline(device_length, df = 0, method = "AIC"), data = train1)
summary(fit5) # p=0 (original = 0.0065304314223657567)
fit6 <- coxph(Surv(time_until_answer, answered) ~ sqrt(device_length), data = train1)
summary(fit6) # p=0.0002291 (lower p-value than without sqrt)

# newline_ratio
fit7 <- coxph(Surv(time_until_answer, answered) ~ pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
summary(fit7) # p=0.00000000008754 (original = 0.0000001398791481533)

fit8 <- coxph(Surv(time_until_answer, answered) ~ sqrt(newline_ratio), data = train1)
summary(fit8) # p=0.00000000001149
AIC(fit8, k = 2) # 65890.28

# avg_tag_length
fit9 <- coxph(Surv(time_until_answer, answered) ~ pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
summary(fit9) # p=0.009088 (original = 0.05)
fit10 <- coxph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_length), data = train1)
summary(fit10) # p=0.1278

# avg_tag_score
fit10 <- coxph(Surv(time_until_answer, answered) ~ pspline(avg_tag_score, df = 0, method = "AIC"), data = train1)
summary(fit10) # p=0.0000000002831
fit11 <- coxph(Surv(time_until_answer, answered) ~ sqrt(avg_tag_score), data = train1)
summary(fit11) # p=0.00000000003211 (original = 0.0000000166232489995)
```
